GO enrichment

### 2022-03-10 analysis/GO_and_ortho.Rmd
GO-term updates! more groups! for the price of one!

```{r setup}
library(tidyverse)

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

```{r fig.width=8, fig.height=10}
sum2 <- seagrass_venn / (plot_list$GO_results_genes_union_Aquatics_and_Seagrasses_NOT_Terrestrials.csv + theme(legend.position="bottom")) +  plot_annotation(tag_levels = 'A') +plot_layout(heights=c(1.5,1))
sum2
cowplot::save_plot(sum2, filename = 'output/patchwork_seagrass_gene_loss.png', base_height = 10, base_width = 8)
```

>>>>

```{r setup}
library(tidyverse)
library(patchwork)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

```{r fig.width=8, fig.height=10}
sum2 <- seagrass_venn / (plot_list$GO_results_genes_in_all_seagrasses_vs_seagrassesBackground_intersect.csv + theme(legend.position="bottom")) +  plot_annotation(tag_levels = 'A') +plot_layout(heights=c(1.5,1))
sum2
cowplot::save_plot(sum2, filename = 'output/patchwork_seagrass_gene_loss.png', base_height = 10, base_width = 8)
```

### 2022-03-10 analysis/GOenrichment.Rmd
GO-term updates! more groups! for the price of one!

@@

```{r eval=FALSE}
compare('Lost_present_gene_lists/Genes_lost_in_A_antarctica_not_other_seagrasses.txt', 'output/GO_results_genes_lost_A_antarctica_not_other_seagrasses.csv', sallgenes, sannAT)

@@

```{r eval=FALSE}
compare('Lost_present_gene_lists/Genes_only_in_Z_marina_not_other_seagrasses.txt', 'output/GO_results_genes_only_Z_marina_not_other_seagrasses.csv', sallgenes, sannAT)

>>>>

# Genes only in seagrasses- seagrass-specific
compare('Lost_present_gene_lists/Genes_in_all_seagrasses_intersect.txt', 'output/GO_results_genes_in_all_seagrasses_vs_backgroundAll_intersect.csv', allgenes, annAT)

compare('Lost_present_gene_lists/Genes_in_all_seagrasses_union.txt', 'output/GO_results_genes_in_all_seagrasses_vs_backgroundAll_union.csv', allgenes, annAT)

@@

```{r eval=FALSE}

compare('Lost_present_gene_lists/Genes_lost_in_A_antarctica_not_other_seagrasses.txt', 'output/GO_results_genes_lost_A_antarctica_not_other_seagrasses.csv', sallgenes, sannAT)

@@

```{r eval=FALSE}
compare('Lost_present_gene_lists/Genes_in_all_seagrasses_intersect.txt', 'output/GO_results_genes_in_all_seagrasses_vs_seagrassesBackground_intersect.csv', sallgenes, sannAT)

compare('Lost_present_gene_lists/Genes_in_all_seagrasses_union.txt', 'output/GO_results_genes_in_all_seagrasses_vs_seagrassesBackground_union.csv', sallgenes, sannAT)

compare('Lost_present_gene_lists/Genes_only_in_Z_marina_not_other_seagrasses.txt', 'output/GO_results_genes_only_Z_marina_not_other_seagrasses.csv', sallgenes, sannAT)
